Dynamic Adaptive Saturated Sliding Mode Control For Deployment of Tethered Satellite System

### 2016-10-31 manuscript.tex
20161031

@@

The simulation results of the deployment dynamics subjected to uncertainties are exhibited from Fig~\ref{fig:7} to Fig~\ref{fig:10}. In Fig~\ref{fig:7}, although there exist parametric uncertainties compared with Figs~\ref{fig:3}-\ref{fig:6}, QST-SMC still performs the deployment with the shortest rise time and the minimum overshoot among the three methods, and the tethers are deployed to the desired position at about 8 $rad$ by observing the dynamics of the in-plane and out-of-plane angles from Fig~\ref{fig:9}. In addition, the result in Fig~\ref{fig:10} shows that the tension falls in the reasonable region, and meanwhile the chattering of the input in the stable status is eliminated by utilizing the boundary layer technique. Hence, the robustness of the proposed control laws can guarantee the stability of the deployment subjected to uncertainties and disturbances.}

>>>>

\textcolor{red}{For the adaptive sliding mode control with input limitation, the adaptive update rate $\frac{d}{dt}F(t)$ always helps to remove the side-effect of the input limitation during the stability analysis by using Lyapunov second method, and moreover, the actual examples of $F(t)$ are unhelpful to the theoretical derivation and the controller design~\cite{Hu2008552,6060930}. This is because we can search the actual value of $F(t)$  by the way of state updating from the initial condition $F(0)=0$, for instance, in our simulations, we applied ode45 technique to update states of the overall system including this adaptive update rate.}

@@

The simulation results of the deployment dynamics subjected to uncertainties are exhibited from Fig~\ref{fig:7} to Fig~\ref{fig:10}. In Fig~\ref{fig:7}, although there exist parametric uncertainties compared with Figs~\ref{fig:7}-\ref{fig:9}, QST-SMC still performs the deployment with the shortest rise time and the minimum overshoot among the three methods, and the tethers are deployed to the desired position at about 8 $rad$ by observing the dynamics of the in-plane and out-of-plane angles from Fig~\ref{fig:9}. In addition, the result in Fig~\ref{fig:10} shows that the tension falls in the reasonable region, and meanwhile the chattering of the input in the stable status is eliminated by utilizing the boundary layer technique. Hence, the robustness of the proposed control laws can guarantee the stability of the deployment subjected to uncertainties and disturbances.}
